\documentclass[10pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\author{Jacques van Wyk}
\title{Background}

\begin{document}
	\section{Background}
	
	We had a meeting with our client Ms Pieterse on Wednesday, 17 February 2016.
 	Our client requires the implementation of a system which will allow researchers to keep
 	track of their publications.
 	\newline
 	\newline
 	We have been given this topic for our mini project for the module COS 301. Furthermore, the 	mini-project is to train us and help us be more ready for the main project of this module.
 	\newline
 	\newline
 	This gives our group, team Fox, the opportunity to gain experience on how to put together
    a SRS (Software Requirements Specification) that will help us and the client to better
    understand what they want the system and its' functionality to be and how they 
    would like to interact with the system. Consequently, if we better understand what our
    client wants the system to be, it will give us a better opportunity to implement a system
    that the client will be pleased with and which the client will want to use.
 	\newline
 	\newline
 	In addition, the system will be used by the Computer Science department at the University
 	of Pretoria. Hopefully the system will improve on a system(s) currently in use and will
 	provide a basic structure of good quality which will enable it to be updated and improved
 	in the future of its' software development life cycle.
 	\newline
 	\newline
 	Furthermore, the project might serve as an example to other students on how to implement
 	such a system or it can be used as a basic structure and starting point for other
 	institutes.
 	
\end{document}