\documentclass{article}
\usepackage[utf8]{inputenc}

\title{Introduction}
\author{Jason Gordon}
\date{February 2016}

\begin{document}

\maketitle
\section{Introduction}
This is the Software Requirements specification document for the system to keep record of research papers in the Computer Science Department of the University of Pretoria.
This document includes sections such as:
\begin{enumerate}
    \item Vision for the system
\begin{itemize}
    \item This includes the projected vision and outcomes of the system and what the Computer Science Department aims to achieve with this project. 
\end{itemize}

    \item Background to why the system is being developed

\begin{itemize}
    \item This includes a discussion of the problem which the Computer Science Department is faced with in regard to keeping track of their research papers and how this system will find a solution to the problem being faced. 
\end{itemize}

    \item Architecture Requirements
\setlength{\parindent}{2.5em}

\begin{itemize}
    \item This includes how the system will be accessed by the users of the system and through which platforms this will be done. Additionally the quality requirements of the system will be discussed as well as what external systems will be used to put this system together. Lastly it will include any constraints that the client has specified with regard to what must be used in the system. 
\end{itemize}

    \item Functional requirements and application design

\begin{itemize}
    \item This will include the functionality of the system that is required by the users of the system. 
\end{itemize}
    \item Open Issues
\begin{itemize}
    \item This section will discuss any requirements of the system that may be unclear or has not been specified. It will also include any inconsistencies that have been discovered in the requirements. 
\end{itemize}
\end{enumerate}

\end{document}